---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fbadstats

R Package for generating statistics from Facebook ads performance data. Currently only includes the breakdown Group analyzer function `fbadGstats`.

## Installation

First install the free (open-source) statistical software (and language) named "R" at:
[http://cran.rstudio.com/](http://cran.rstudio.com/)

Then download the most popular software to make using R easier, RStudio. The free version will be perfect. Scroll down and choose the appropriate installer under **Installers for Supported Platforms** at:
[https://www.rstudio.com/products/rstudio/download/](https://www.rstudio.com/products/rstudio/download/)

Open RStudio and you can now install the `fbadstats` package from github by entering the following in RStudio:
```{r gh-installation, eval = FALSE}
## This first package is to enable the install_github function
install.packages("devtools")
## Now we can always load that package with
library("devtools")
## Install fbadstats
devtools::install_github("RickPack/fbadstats")
```

## Example 1/n
```{r example, fig.width = 10, fig.height = 4.5, fig.align = 'center'}
## Load fbadstats
library("fbadstats")
# Show only the best performing groups and include the graphical output
fbadGstats(filerd = "example_DMA.csv", grphout = "YES", tblout = "BEST")
```
## For A:B comparison, use the filtervar parameter. 
## Here we see BOTH [default for tblout parameter] the top 3 and worst 3 Age / Gender groups in a comparison between where "6txt" did and did not appear in the ad set name
## At least two events (clicks) must have occurred. Otherwise an anomalous single event for 25-34 males causes that group to appear.
## "Hotreg" indicated where selected regions with a history of performing well were the only ones targeted with the advertisement
```{r example, fig.width = 10, fig.height = 4.5, fig.align = 'center'}
fbadGstats(filerd = "example_PerfClk_AgeGender.csv", filtervar = 'hotreg',    prtrow = 3, minevent = 2, grphout = "NO")
fbadGstats(filerd = "example_PerfClk_AgeGender.csv", filtervarneg = 'hotreg', prtrow = 3, minevent = 2,   grphout = "NO")
```
## Assign fbadGstats call to a variable in order to explore the data outside of fbadGstats
```{r example, fig.width = 10, fig.height = 4.5, fig.align = 'center'}
myfbfrm <- fbadGstats(filerd = "example_PerfClk_AgeGender.csv", filtervar = 'AllPg', grphout = "NO")
## What are all of the available ad set names?
# 1. First look at the column names in the data
colnames(myfbfrm)
# 2. Now we can use the unique function to see all of the available names and appropriately adjust the filtervar parameter
unique(myfrmfrm$Ad.Set.Name)
```
**Note**: See more examples by entering in RStudio:
```{r, eval = FALSE}
vignette(package = "fbadstats")
```
